%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

* Indicates equal contribution

%---------------------------------------------------------
  \cvpublicationentry
    {Exemplars in Africa: Evaluating the impact of the 100 Mille Etudiants program to increase adoption of protective behaviors against COVID-19 in Dakar, Senegal.} % Title
    {\textbf{D. Mistry}, L. A. Skrip, N. Noori, M. Sall, I. Ba, A. Oron, and B. M. Althouse.} % Authors
    {} % Journal
    {} % Volume
    {} % Issue
    {} % Pages
    {} % Year
    {Manuscript in progress.} % Notes
    {} % URL
    \vspace{1.5mm}

%---------------------------------------------------------
  \cvpublicationentry
    {SynthPops: A Generative Model of Synthetic Contact Networks.} % Title
    {\textbf{D. Mistry}, C. C. Kerr, and D. J. Klein.} % Authors
    {} % Journal
    {} % Volume
    {} % Issue
    {} % Pages
    {} % Year
    {Manuscript in progress.} % Notes
    {} % URL
    \vspace{1.5mm}

%---------------------------------------------------------
  \cvpublicationentry
    {Controlling SARS-CoV-2 via test-trace-quarantine.} % Title
    {C. C. Kerr, \textbf{D. Mistry},  R. M. Stuart, K. Rosenfeld, G. R. Hart, P. Selvaraj, R. C. N\'{u}\~{n}ez, J. A. Cohen, R. G. Abeysuriya, L. George, B. Hagedorn, M. Jastrzebski, M. Fagalde, J. Duchin, M. Famulare, and D. J. Klein.} % Authors
    {} % Journal
    {} % Volume
    {} % Issue
    {} % Pages
    {} % Year
    {Manuscript under review.} % Notes
    {\href{https://www.medrxiv.org/content/10.1101/2020.07.15.20154765v3}{https://www.medrxiv.org/content/10.1101/2020.07.15.20154765v3}} % URL
    \vspace{1.5mm}


%---------------------------------------------------------
  \cvpublicationentry
    {Modelling the impact of reducing control measures on the COVID-19 pandemic in a low transmission setting.} % Title
    {N. Scott, A. Palmer, D. Delport, R. G. Abeysuriya, R. M. Stuart, C. C. Kerr, \textbf{D. Mistry}, D. J. Klein, R. Sacks-Davis, K. Heath, S. Hainsworth, A. Pedrana, M. Stoove, D. P. Wilson, M. Hellard.} % Authors
    {} % Journal
    {} % Volume
    {} % Issue
    {} % Pages
    {} % Year
    {Manuscript under review.} % Notes
    {\href{https://www.medrxiv.org/content/10.1101/2020.06.11.20127027v1}{https://www.medrxiv.org/content/10.1101/2020.06.11.20127027v1}} % URL
    \vspace{1.5mm}

%---------------------------------------------------------
  \cvpublicationentry
    {Covasim: an agent-based model of COVID-19 dynamics and interventions.} % Title
    {C. C. Kerr, R. M. Stuart, \textbf{D. Mistry}, R. G. Abeysuriya, G. R. Hart, K. Rosenfeld, P. Selvaraj, R. C. Núñez, B. Hagedorn, L. George, A. Izzo, A. Palmer, D. Delport, C. Bennette, B. Wagner, S. Chang, J. A Cohen, J. Panovska-Griffiths, M. Jastrzebski, A. P. Oron, E. Wenger, M. Famulare, D. J. Klein.} % Authors
    {} % Journal
    {} % Volume
    {} % Issue
    {} % Pages
    {} % Year
    {} % Notes
    {\href{https://www.medrxiv.org/content/10.1101/2020.05.10.20097469v1}{https://www.medrxiv.org/content/10.1101/2020.05.10.20097469v1}} % URL
    \vspace{1.5mm}

%---------------------------------------------------------
  \cvpublicationentry
    {Seeding COVID-19 across sub-Saharan Africa: an analysis of reported importation events across 40 countries.} % Title
    {L. A. Skrip, P. Selvaraj, B. Hagedorn, A. L. Ouédraogo, N. Noori, \textbf{D. Mistry}, J. Bedson, L. Hébert-Dufresne, S. V. Scarpino, B. M. Althouse.} % Authors
    {} % Journal
    {} % Volume
    {} % Issue
    {} % Pages
    {} % Year
    {Manuscript under review.} % Notes
    {\href{https://www.medrxiv.org/content/10.1101/2020.04.01.20050203v2}{https://www.medrxiv.org/content/10.1101/2020.04.01.20050203v2}} % URL
    \vspace{1.5mm}

%---------------------------------------------------------
  \cvpublicationentry
    {Determining the optimal strategy for reopening schools, work and society in the UK: balancing earlier opening and the impact of test and trace strategies with the risk of occurrence of a secondary COVID-19 pandemic wave.} % Title
    {J. Panovska-Griffiths, C. C. Kerr, R. M. Stuart, \textbf{D. Mistry}, D. J. Klein, R. M. Viner, C. Bonell.} % Authors
    {Lancet Child Adolesc Health} % Journal
    {} % Volume
    {} % Issue
    {} % Pages
    {} % Year
    {} % Notes
    {\href{https://doi.org/10.1016/S2352-4642(20)30250-9}{https://doi.org/10.1016/S2352-4642(20)30250-9}} % URL
    \vspace{1.5mm}

%---------------------------------------------------------
  \cvpublicationentry
    {Spread of infectious disease and social awareness as parasitic contagions on clustered networks.} % Title
    {L. Hébert-Dufresne, \textbf{D. Mistry}, B. M. Althouse.} % Authors
    {} % Journal
    {} % Volume
    {} % Issue
    {} % Pages
    {} % Year
    {Manuscript under review.} % Notes
    {\href{https://arxiv.org/pdf/2003.10604.pdf}{https://arxiv.org/pdf/2003.10604.pdf}} % URL
    \vspace{1.5mm}

%---------------------------------------------------------
  \cvpublicationentry
    {Inferring high-resolution human mixing patterns for disease modeling.} % Title
    {\textbf{D. Mistry}, M. Litvinova, A. Pastore y Piontti, M. Chinazzi, L. Fumanelli, M. F. C. Gomes, S. A. Haque, Q. Liu, K. Mu, X. Xiong, M. E. Halloran, I. M. Longini, S. Merler, M. Ajelli, A. Vespignani.} % Authors
    {} % Journal
    {} % Volume
    {} % Issue
    {} % Pages
    {} % Year
    {Manuscript under review.} % Notes
    {\href{https://arxiv.org/abs/2003.01214}{https://arxiv.org/abs/2003.01214}} % URL
    \vspace{1.5mm}

%---------------------------------------------------------
  \cvpublicationentry
    {Characterizing the global spread of epidemics and their predictability through human mobility networks.} % Title
    {\textbf{D. Mistry}, K. Sun, A. Pastore y Piontti, M. F. C. Gomes, L. Rossi, A. Vespignani.} % Authors
    {} % Journal
    {} % Volume
    {} % Issue 
    {} % Pages
    {} % Year
    {Manuscript in progress.} % Notes
    {} % URL
    \vspace{1.5mm}

%---------------------------------------------------------
  \cvpublicationentry
    {Quantifying the risk of Zika virus local transmission in the continental US during the 2015-2016 ZIKV epidemic.} % Title
    {K. Sun, Q. Zhang, A. Pastore-Piontti, M. Chinazzi, \textbf{D. Mistry}, N. E. Dean, D. P. Rojas, S. Merler, P. Poletti, L. Rossi, M. E. Halloran, I. M. Longini, A. Vespignani.} % Authors
    {BioMed Central Medicine. } % Journal
    { 16.} % Volume
    { 1. } % Issue 
    { 195.} % Pages
    {2018.} % Year
    {} % Notes
    {\href{https://doi.org/10.1186/s12916-018-1185-5}{https://doi.org/10.1186/s12916-018-1185-5}} % URL
    \vspace{1.5mm}

%---------------------------------------------------------
  \cvpublicationentry
    {Spreading of Zika virus in the Americas.} % Title
    {Q. Zhang, K.Sun, M. Chinazzi, A. Pastore-Piontti, N. E. Dean, D. P. Rojas, S. Merler, \textbf{D. Mistry}, P. Poletti, L. Rossi, M. Bray, M. E. Halloran, I. M. Longini, A. Vespignani.} % Authors
    {Proceedings of the National Academy of Sciences. } % Journal
    { 114.} % Volume
    { 22. } % Issue 
    {  E4334-E4343. } % Pages
    { 2017.} % Year
    {} % Notes
    {\href{https:/doi.org/10.1073/1620161114}{https:/doi.org/10.1073/1620161114}} % URL
    \vspace{1.5mm}

%---------------------------------------------------------
  \cvpublicationentry
    {Committed activists and the reshaping of status-quo social consensus.} % Title
    {\textbf{D. Mistry}, Q. Zhang, N. Perra, A. Baronchelli.} % Authors
    {Phys. Rev. E.} % Journal
    { 92.} % Volume
    { } % Issue 
    {042805. } % Pages
    { 2015.} % Year
    {} % Notes
    {\href{https:/doi.org/10.1103/PhysRevE.92.042805}{https:/doi.org/10.1103/PhysRevE.92.042805}} % URL
    \vspace{1.5mm}

%---------------------------------------------------------
\end{cventries}
